Examples of Customization

### 2016-08-09 custom_examples.Rmd
Fixing sim_exposure to include default parameters

```{r}
sintrend <- function(n, y){
  day <- c(1:n)
  1 + y * sin(2 * pi * (day / 365))
}
calc_t(n = 5, y = .3, trend = "custom", custom_func = sintrend)
plot(calc_t(1000, y = .3, trend = "custom", custom_func = sintrend))
```

>>>>

```{r}
sintrend <- function(n, y){
  day <- c(1:n)
  base <- 1 + y * sin(2 * pi * (day / 365))
  rnorm(n, mean = base, sd = 1)
}
calc_t(n = 5, y = .3, trend = "custom", custom_func = sintrend)
plot(calc_t(1000, y = .3, trend = "custom", custom_func = sintrend))
```
